---
title: 'QuantModelling: Assignment'
output:
  pdf_document: default
  html_document: default
  word_document: default
Description: Solving linear equation using R
---
#Title - Linear Programming with R
#Name - Surbhi Khandelwal

For This Problem:
Objective function
min: +22 A1 +14 A2 +30 A3 +600 A1+ 600 A2+ 600 A3 + 16 B1 +20 B2 +24 B3 + 625 B1 + 625 B2 + 625 B3;

(Cost of Shipping per product + cost of production for each product)

Constraints:
W1Demand: +A1 +B1 = 80;
W2Demand: +A2 +B2 = 60;
W3Demand: +A3 +B3 = 70;
ASupply: +A1 +A2 +A3 <= 100;
BSupply: +B1 +B2 +B3 <= 120;

Where:
A1 - Production at Plant A and being shipped to Warehouse 1
A2 - Production at Plant A and being shipped to Warehouse 2
A3 - Production at Plant A and being shipped to Warehouse 3
B1 - Production at Plant B and being shipped to Warehouse 1
B2 - Production at Plant B and being shipped to Warehouse 2
B3 - Production at Plant B and being shipped to Warehouse 3


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo= TRUE)
```

```{r comment=NA }
library(lpSolve)
library(lpSolveAPI)
#install.packages('tinytex')
#tinytex::install_tinytex()
y <- read.lp("Ass6.lp")
y
```

Solving the problem to get objective function and do sensitivity and dual analysis. 
```{r}
solve(y)
get.objective(y)
get.variables(y)
get.constraints(y)
get.sensitivity.objex(y)
get.sensitivity.rhs(y)
```