---
title: 'QuantModelling: Assignment 10'
output:
  pdf_document: default
  html_document: default
  word_document: default
Description: Goal Programming
---
#Title - Integer Programming  
#Name - Surbhi Khandelwal  



AP is a shipping service that guarantees overnight delivery of packages in the continental US.
The company has various hubs at major cities and airports across the country. Packages are
received at hubs, and then shipped to intermediate hubs or to their final destination.
The manager of the AP hub in Cleveland is concerned about labor costs, and is interested in
determining the most effective way to schedule workers. The hub operates seven days a week,
and the number of packages it handles varies from one day to another. The table below provides
an estimate of the number of workers needed each day of the week.


*
#Xi = the number of workers assigned to shift i, i=1 ,7

Min 775X1 +800X2 +800X3 +800X4 +800X5 +775X6 +750X7

ST

      X2+ X3+ X4+ X5+ X6     >= 18 } Sunday
    
          X3+ X4+ X5+ X6+ X7 >= 27 } Monday
        
  X1+         X4+ X5+ X6+ X7 >= 22 }Tuesday

  X1+ X2+         X5+ X6+ X7 >= 26 } Wednesday
  
  X1+ X2+ X3+         X6+ X7 >= 25 } Thursday
  
  X1+ X2+ X3+ X4+         X7 >= 21 } Friday
  
  X1+ X2+ X3+ X4+ X5         >= 19 } Saturday
  
  Xi >= 0  and integer for all i 



### Min 775X1 +800X2 +800X3 +800X4 +800X5 +775X6 +750X7

### Constraints:
    X2+ X3+ X4+ X5+ X6     >= 18 } Sunday
    
        X3+ X4+ X5+ X6+ X7 >= 27 } Monday
        
X1+         X4+ X5+ X6+ X7 >= 22 }Tuesday

X1+ X2+         X5+ X6+ X7 >= 26 } Wednesday

X1+ X2+ X3+         X6+ X7 >= 25 } Thursday

X1+ X2+ X3+ X4+         X7 >= 21 } Friday

X1+ X2+ X3+ X4+ X5         >= 19 } Saturday

Xi >= 0  and integer for all i 

### where
X1 = shift 1 with Sunday and Monday off

X2 = shift 2 with Monday and Tuesday off

X3 = shift 3 with Tuesday and Wednesday off

X4 = shift 4 with Wednesday and Thursday off

X5 = shift 5 with Thursday and Friday off

X6 = shift 6 with Friday and Saturday off

X7 = shift 7 with Saturday and Sunday off

#To find the constraint value for Profit, we need to first run the lp for it.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo= TRUE)
```

```{r comment=NA }
library(lpSolve)
library(lpSolveAPI)
y <- read.lp("ass10.lp")
y
```

Solving the problem to get objective function. 
```{r}
solve(y)
get.objective(y)

```
#Our Objective function is: 25675.
#Let's look at the variables to understand what this means.

```{r}

get.variables(y)
```


### What this shows is:
#X1 = shift 1 with Sunday and Monday off = 2
#X2 = shift 2 with Monday and Tuesday off = 4
#X3 = shift 3 with Tuesday and Wednesday off = 5
#X4 = shift 4 with Wednesday and Thursday off = 0
#X5 = shift 5 with Thursday and Friday off = 8
#X6 = shift 6 with Friday and Saturday off = 1
#X7 = shift 7 with Saturday and Sunday off = 13

### Our objective function = 2x775 + 4x800 + 5x800 + 8x800 + 1X775 + 13x750 = 25675.
### The minimum cost that we can spend on salaries is 25675.