---
title: "Assignment 8 - DEA Analysis"
name: " Surbhi Khandelwal"
output:
  pdf_document: default
  html_notebook:
    highlight: textmate
    theme: cerulean
  html_document:
    df_print: paged
---

```{r setup, include=FALSE, comment=NA}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```

##                                 Surbhi Khandelwal
***
The Hope Valley Health Care Association owns and operates six nursing homes in adjoining
states. An evaluation of their efficiency has been undertaken using two inputs and two outputs.
The inputs are staffing labor (measured in average hours per day) and the cost of supplies (in
thousands of dollars per day). The outputs are the number of patient-days reimbursed by third party sources and the number of patient-days reimbursed privately. 


### Let us now calculate the weights to achieve the efficiency values for each nursing home

#### Loading all the packages.

```{r comments=NA}
#install.packages("Benchmarking")
library(Benchmarking)
library(tidyverse)
library(dplyr)
```

Our problem has 6 Nursing Homes with   
2 inputs: staff Hours per day and supplies per day   
2 outputs: Reimbursed Patient-days, Privately Paid patient-days.  

```{r}
input <- matrix(c(150,400,320,520,350,320, 0.2,0.7, 1.2,2.0,1.2,0.7),ncol=2)
output <- matrix(c(14000,14000,42000,28000,19000,14000, 3500,21000, 10500,42000,25000,15000),ncol = 2)
colnames(input) <- c("Staff Hours/day","Supplies/day")
colnames(output) <- c("ReimursedPateients","Privately Paid Patients")
main <- cbind(input, output)
main

```


We now run the DEA analysis.

\newpage

# DEA Analysis with FDH
```{r}
e1 <- dea(input,output,RTS = "fdh")            # provide the input and output 

effdh<- eff(e1)                            # put efficiency in a dataset

p1<- peers(e1)                    # identify the peers

colnames(p1)[1] <- "FDH_peer1"

l1<- lambda(e1)                            # identify the relative weights given to the peers

colnames(l1)[1] <- "FDH_L1"
colnames(l1)[2] <- "FDH_L2"
colnames(l1)[3] <- "FDH_L3"
colnames(l1)[4] <- "FDH_L4"
colnames(l1)[5] <- "FDH_L5"
colnames(l1)[6] <- "FDH_L6"

dea.plot(input,output,RTS="fdh",ORIENTATION="in-out",txt=rownames(input),main="FDH Plot")  # plot the results

table1<- cbind(main,p1,l1,effdh)             #Summarised table
table1

```

### This Model suggests that all the Nursing Branches are efficient.

\newpage
# DEA Analysis with CRS
```{r}
e2 <- dea(input,output,RTS = "crs")            # provide the input and output 

efcrs<- eff(e2)

p2<- peers(e2)                    # identify the peers

colnames(p2)[1] <- "CRS_peer1"
colnames(p2)[2] <- "CRS_peer2"
colnames(p2)[3] <- "CRS_peer3"

l2<- lambda(e2)                            # identify the relative weights given to the peers

colnames(l2)[1] <- "CRS_L1"
colnames(l2)[2] <- "CRS_L2"
colnames(l2)[3] <- "CRS_L3"
colnames(l2)[4] <- "CRS_L4"

dea.plot(input,output,RTS="crs",ORIENTATION="in-out",main="CRS Plot")         # plot the results
table2<- cbind(main,p2,l2,efcrs)            #Summarize the result
table2

```

### The result indicates that Nursing branches 1,2,3 and 4 are efficient.
### Efficiency of Nursing Branch 5 is 97.74% and of Branch 6 is 86.74%.
### Branch 5 has 1, 2, and 4 as it's peers with relative weight of 0.2, 0.08, and 0.53.
### Branch 6 has 1, 2, and 4 as it's peers with relative weight of 0.34, 0.39, and 0.13.


\newpage
# DEA Analysis with VRS
```{r}
e3 <- dea(input,output,RTS = "vrs")            # provide the input and output 

efvrs<- eff(e3)

p3<- peers(e3)                    # identify the peers

colnames(p3)[1] <- "VRS_peer1"
colnames(p3)[2] <- "VRS_peer2"
colnames(p3)[3] <- "VRS_peer3"

l3<- lambda(e3)                            # identify the relative weights given to the peers

colnames(l3)[1] <- "VRS_L1"
colnames(l3)[2] <- "VRS_L2"
colnames(l3)[3] <- "VRS_L3"
colnames(l3)[4] <- "VRS_L4"
colnames(l3)[5] <- "VRS_L5"

dea.plot(input,output,RTS="vrs",ORIENTATION="in-out",txt=rownames(input), main="VRS Plot")     # plot the results

table3<- cbind(main,p3,l3,efvrs)
table3


```

### The result indicates that Nursing branches 1,2,3,4 and 5 are efficient.
### Efficiency of Nursing Branch 6 is 89.63%.
### Branch 6 has 1, 2, and 5 as it's peers with relative weight of 0.4, 0.34, and 0.25.


\newpage
# IRS
```{r}
e4 <- dea(input,output,RTS = "irs")            # provide the input and output 

efirs <- eff(e4)

p4<- peers(e4)                    # identify the peers

colnames(p4)[1] <- "IRS_peer1"
colnames(p4)[2] <- "IRS_peer2"
colnames(p4)[3] <- "IRS_peer3"

l4<- lambda(e4)                            # identify the relative weights given to the peers

colnames(l4)[1] <- "IRS_L1"
colnames(l4)[2] <- "IRS_L2"
colnames(l4)[3] <- "IRS_L3"
colnames(l4)[4] <- "IRS_L4"
colnames(l4)[5] <- "IRS_L5"

dea.plot(input,output,RTS="irs",ORIENTATION="in-out",txt=TRUE,main="IRS Plot")    # plot the results

table4<- cbind(main,p4,l4,efirs)
table4


```

### The result indicates that Nursing branches 1,2,3,4 and 5 are efficient.
### Efficiency of Nursing Branch 6 is 89.63%.
### Branch 6 has 1, 2, and 5 as it's peers with relative weight of 0.4, 0.34, and 0.25.

\newpage
# DRS
```{r}
e5 <- dea(input,output,RTS = "drs")            # provide the input and output 

efdrs<- eff(e5)

p5<- peers(e5)                    # identify the peers

colnames(p5)[1] <- "DRS_peer1"
colnames(p5)[2] <- "DRS_peer2"
colnames(p5)[3] <- "DRS_peer3"

l5<- lambda(e5)                            # identify the relative weights given to the peers

colnames(l5)[1] <- "DRS_L1"
colnames(l5)[2] <- "DRS_L2"
colnames(l5)[3] <- "DRS_L3"
colnames(l5)[4] <- "DRS_L4"

dea.plot(input,output,RTS="drs",ORIENTATION="in-out", main="DRS Plot")     # plot the results
table5<- cbind(main,p5,l5,efdrs)
table5

```
### The result indicates that Nursing branches 1,2,3 and 4 are efficient.
### Efficiency of Nursing Branch 5 is 97.74% and of Branch 6 is 86.74%.
### Branch 5 has 1, 2, and 4 as it's peers with relative weight of 0.2, 0.08, and 0.53.
### Branch 6 has 1, 2, and 4 as it's peers with relative weight of 0.34, 0.39, and 0.13.

\newpage
# FRH
```{r comment=NA}
e6 <- dea(input,output,RTS = "add")            # provide the input and output 

effrh <- eff(e6)

p6<- peers(e6)                    # identify the peers

colnames(p6)[1] <- "FRH_peer1"

l6<- lambda(e6)                            # identify the relative weights given to the peers

colnames(l6)[1] <- "FRH_L1"
colnames(l6)[2] <- "FRH_L2"
colnames(l6)[3] <- "FRH_L3"
colnames(l6)[4] <- "FRH_L4"
colnames(l6)[5] <- "FRH_L5"
colnames(l6)[6] <- "FRH_L6"

dea.plot(input,output,RTS="add",ORIENTATION="in-out",txt=rownames(input),main="FRH/ADD Plot ")
table6<- cbind(main,p6,l6,effrh)
table6

```
### According to this model, all the Nursing Branches are efficient.

## Let's look at the efficiencies of all the models to compare them
```{r}
effic <- cbind(effdh,efcrs,efvrs,efirs,efdrs,effrh)
effic
```

## So Looking at this we see that our model performs very similarly for:
FDH and FRH
CRS and DRS
VRS and IRS


In VRS, we can look at what will happen if we rescale a firm.
In VRS, there are 2 possibilities:
If we increase the input and the output increases - This is Constant Return to Scale.
If we decrease the input and the output decreases - Decreasing Return to Scale.


Comparing CRS and VRS
CRS - determined by the highest achievable ratio of outputs to inputs in
the sample, regardless of size.

VRS - passes through the points where the Nursing Homes have the highest output to input ratios, given their relative size, then runs parallel to the respective axes beyond the extreme points.

Mostly the efficiency scores calculated under variable returns, VRS, will be higher than or equal to those obtained under constant returns,CRS. Which we can observe in our output.

When Efficiency score = 1, VRS and CRS coincide.

IRS, Increasing returns to scale shows a proportional increase in all inputs causes outputs to increase by a greater proportion.

FDH model relaxes the convexity assumption of basic DEA models. The efficiency scores of FDH input-oriented model are always greater than the ones of input-oriented variable returns to scale(VRS) model. We can easily see this in our output also, where we have efficiency score as 1 for all the Nursing Homes but it's not the same with efficiency scores for VRS. 

Because of this above relationship: The production possibility set of FDH model is subset of VRS model as well as CRS model.

FRH model permits input and output to enter in only discrete amounts. It's helpful when we want to use mixed integer programming type.