---
title: "QuantModelling: Assignment"
output: html_document
Description: Solving linear equation using R
---
Title - Linear Programming with R
Name - Surbhi Khandelwal

I have solved the problem using 2 different methods. One as you had shown and another using matrices. 
Just wanted to mention all the decision variables, objective function, and constraints of the problem:

L1  =  number of large units produced per day at Plant 1, 
M1  =  number of medium units produced per day at Plant 1,
S1  =  number of small units produced per day at Plant 1,
L2  =  number of large units produced per day at Plant 2, 
M2  =  number of medium units produced per day at Plant 2,
S2  =  number of small units produced per day at Plant 2,
L3  =  number of large units produced per day at Plant 3, 
M3  =  number of medium units produced per day at Plant 3,
S3  =  number of small units produced per day at Plant 3.

Objective function:

Maximize:   	420 L1 + 360 M1 + 300 S1 + 420 L2 + 360 M2 + 300 S2 + 420 L3 + 360 M3 + 300 S3,

Subject To:
		          L1 + M1 + S1   <=    750   (P1Cap)
		          
              L2 + M2 + S2   <=    900   (P2Cap)
              
              L3 + M3 + S3   <=    450   (P3Cap)

              20 L1 + 15 M1 + 12 S1   <=    13000    (P1SqFoot)
              
              20 L2 + 15 M2 + 12 S2   <=    12000    (P2SqFoot)
              
              20 L3 + 15 M3 + 12 S3   <=    5000     (P3SqFoot)
              
              L1 + L2 + L3     <=      900    (LSales)
              
              M1 + M2 + M3     <=      1200   (MSales)
              
              S1 + S2 + S3     <=      750    (SSales)
              
              1/750(L1 + M1 + S1) -  1/900(L2 + M2 + S2) = 0   (EC1)
              
              1/750(L1 + M1 + S1) -  1/450(L3 + M3 + S3) = 0   (EC2)
              
              1/900(L2 + M2 + S2) -  1/450(L3 + M3 + S3) = 0   (EC3)
(nonnegative)
L1 >= 0, M1 >= 0, S1 >= 0, L2 >= 0, M2 >= 0, S2 >= 0, L3 >= 0, M3 >= 0, S3 >= 0.


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo= TRUE)
```

```{r comment=NA }
library(lpSolve)
library(lpSolveAPI)

#Stating that there are 0 constraints and 9 decision variables.
sol <- make.lp(0, 9)

# Now create the objective function. The default is a minimization problem. 
set.objfn(sol, c(420,360,300,420,360,300,420,360,300))

# As the default is a minimization problem, we change the direction to set maximization
lp.control(sol,sense='max')

# Add the constraints
add.constraint(sol, c(1,1,1,0,0,0,0,0,0), "<=", 750)
add.constraint(sol, c(0,0,0,1,1,1,0,0,0), "<=", 900)
add.constraint(sol, c(0,0,0,0,0,0,1,1,1), "<=", 450)
add.constraint(sol, c(20,15,12,0,0,0,0,0,0), "<=", 13000)
add.constraint(sol, c(0,0,0,20,15,12,0,0,0), "<=", 12000)
add.constraint(sol, c(0,0,0,0,0,0,20,15,12), "<=", 5000)
add.constraint(sol, c(1,0,0,1,0,0,1,0,0), "<=", 900)
add.constraint(sol, c(0,1,0,0,1,0,0,1,0), "<=", 1200)
add.constraint(sol, c(0,0,1,0,0,1,0,0,1), "<=", 750)
add.constraint(sol, c(900,900,900,-750,-750,-750,0,0,0), "=", 0)
add.constraint(sol, c(450,450,450,0,0,0,-750,-750,-750), "=", 0)
add.constraint(sol, c(0,0,0,450,450,450,-900,-900,-900), "=", 0)

#set.bounds(lprec, upper =  c(750,750,750,900,900,900,450,450,450), columns = c(1, 2,3,4,5,6,7,8,9))
#set.bounds(lprec, upper =  c(900,1200,750,900,1200,750,900,1200,750), columns = c(1, 2,3,4,5,6,7,8,9))

```


```{r def }
RowNames <- c("P1Cap", "P2Cap", "P3Cap","P1SqFoot",
              "P2SqFoot","P3SqFoot","LSales","MSales","SSales","EC1","EC2","EC3")
ColNames <- c("L1", "M1","S1","L2","M2","S2","L3","M3","S3")
dimnames(sol) <- list(RowNames, ColNames)


#Looking at the definition of sol
sol

#Solving the sol
solve(sol)

write.lp(sol, filename = "wgc.lp", type = "lp")

```

```{r res}
#Getting the value of Objective Function and the decision variables
get.objective(sol)
get.variables(sol)
```




We get that value of Objective Function is 696000. This gives the maximum profit we can get basis the constraints.

We should build:
Large size bags in plant 1 - 516
Medium size bags in plant 1 - 177
Medium size bags in plant 2 - 666
Small size bags in plant 2 - 166
Small size bags in plant 3 - 416

Here 's the 2nd Method I have used
```{r set}
#install.packages("lpsolve") Already have this package
library(lpSolve)
```

```{r ass}
#Assign objective function value
f.obj <- c(420,360, 300, 420, 360, 300, 420, 360, 300)
#Assign constraints value
f.con <- matrix(c(1,1,1,0,0,0,0,0,0,
                  0,0,0,1,1,1,0,0,0,
                  0,0,0,0,0,0,1,1,1,
                  20,15,12,0,0,0,0,0,0,
                  0,0,0,20,15,12,0,0,0,
                  0,0,0,0,0,0,20,15,12,
                  1,0,0,1,0,0,1,0,0,
                  0,1,0,0,1,0,0,1,0,
                  0,0,1,0,0,1,0,0,1,
                  900,900,900,-750,-750,-750,0,0,0,
                  450,450,450,0,0,0,-750,-750,-750,
                  0,0,0,450,450,450,-900,-900,-900),nrow = 12,byrow = TRUE)

#Assign value of all operators
f.dir <- c("<=","<=","<=","<=","<=","<=","<=","<=","<=","=","=","=")

#Assign value of RHS
f.rhs <- c(750,
           900,
           450,
           13000,
           12000,
           5000,
           900,
           1200,
           750,
           0,
           0,
           0)

#Calculate objective function
lp("max", f.obj, f.con, f.dir, f.rhs)
lp("max", f.obj, f.con, f.dir, f.rhs)$solution
```